---
title: "PA1_template"
output: html_document
date: "2023-07-04"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducible Research Assignment

## Overview
It is now possible to collect a large amount of data about personal movement using activity monitoring devices such as a [Fitbit](http://www.fitbit.com/), [Nike Fuelband](http://www.nike.com/us/en_us/c/nikeplus-fuelband), or [Jawbone Up](https://jawbone.com/up).

These type of devices are part of the “quantified self” movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. But these data remain under-utilized both because the raw data are hard to obtain and there is a lack of statistical methods and software for processing and interpreting the data.

This assignment makes use of data from a personal activity monitoring device. This device collects data at 5 minute intervals through out the day. The data consists of two months of data from an anonymous individual collected during the months of October and November, 2012 and include the number of steps taken in 5 minute intervals each day.

## Commit Containing Full Submission Requirements

    1. Code for reading in the dataset and/or processing the data
    2. Histogram of the total number of steps taken each day
    3. Mean and median number of steps taken each day
    4. Time series plot of the average number of steps taken
    5. The 5-minute interval that, on average, contains the maximum number of steps
    6. Code to describe and show a strategy for imputing missing data
    7. Histogram of the total number of steps taken each day after missing values are imputed
    8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
    9. All of the R code needed to reproduce the results (numbers, plots, etc.) in the report

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
